Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. \textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} %all the tools perform solar photovoltaic analysis; 

@@

A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}. The PV generator is a semiconductor device that can convert solar energy into DC electricity\textcolor{red}{, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$}. 
For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter). The AC load dictates the behavior of AC electrical load from the house that will be fed by the system. \textcolor{red}{At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.}

>>>>

As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. \textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} \textcolor{green}{how did you conclude that? explain here...} %all the tools perform solar photovoltaic analysis; 

@@

A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}. The PV generator is a semiconductor device that can convert solar energy into DC electricity\textcolor{red}{, with high dependence on two weather variables from the site, where the system is deployed: solar irradiance $G$ and temperature $T$}. 
For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter). The AC load dictates the behavior of AC electrical load from the house that will be fed by the system. \textcolor{red}{In this pictured modular structure, every element produces/consumes current $I$ and voltage $V$, as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct, and $ac$ is alternating signals.}
